Re-fit

### 2022-06-24 scripts/r/04_refit/refit_jvc.Rmd
halfish way

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE, 
  warning = FALSE
  )
knitr::opts_knit$set(root.dir = here::here())
```

```{r}
#| label: libs
library("here")
library("fs")
library("dplyr")
library("tidyr")
library("readr")
library("forcats")
library("ggplot2")
library("stringr")
library("strex")
library("purrr")
library("lme4")
library("brms")
library("broom")
library("broom.mixed")
```

@@

# Functional sequence to get relevant info from Rds files
clean_up <- . %>% 
  tidy(effects = "fixed") %>% 
  suppressWarnings() %>% 
  filter(term %in% c("effect_cattypical", "effect_con")) %>% 
  select(term, estimate, se = std.error)
```

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

# This code will need to change eventually to pull rds files from OSF... for now it assumes they are stored in a folder called "models"
msa_models <- dir_ls(path = here("data", "analyses", "models"), regexp = ".rds$") %>% 
  as_tibble() %>% 
  transmute(path = value, 
    mod_name = str_remove(path, here("data", "analyses", "models/")), 
    mod_name = str_remove(mod_name, ".rds"), 
    model = map(path, ~ readRDS(file = .))) %>% 
  separate(mod_name, 
    into = c("word1", "word2", "mod_n", "outcome", "typicality"), 
    sep = "_", remove = F) %>% 
  unite(group, word1, word2, sep = "_") %>% 
  select(group, mod_name:model) %>% 
  mutate(sum = map(model, clean_up)) %>% 
  suppressWarnings() # because it warns every time that some coef have underscores and its annoying
```

@@

# Simple forest plot of the estimates +/- SE
msa_models %>% 
  unnest(sum) %>% 
  mutate(typicality_lab = if_else(typicality == "cat", 
    "Typicality = categorical", "Typicality = continuous"), 
    mod_name = fct_reorder(mod_name, estimate)) %>% 
  ggplot() + 
  facet_wrap(~ typicality_lab, ncol = 1, scales = "free") + 
  aes(x = estimate, y = mod_name) + 
  geom_segment(aes(x = estimate - se, xend = estimate + se, yend = mod_name), 
    color = "#cc0033", alpha = 0.5, size = 3, lineend = "round") + 
  geom_point(color = "#cc0033", pch = 21, stroke = 3, size = 3.1) + 
  labs(y = "Model", x = "Estimate ± SE") + 
  clean_theme() + 
  theme(strip.text.x = element_text(hjust = 0))
```

>>>>

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE, 
  warning = FALSE
  )

knitr::opts_knit$set(root.dir = here::here())
```

```{r}
#| label: libs
library("here")
library("fs")
library("dplyr")
library("tidyr")
library("readr")
library("readxl")
library("forcats")
library("ggplot2")
library("stringr")
library("strex")
library("purrr")
library("lme4")
library("brms")
library("broom")
library("broom.mixed")
```

@@

# Functional sequence to get relevant info from Rds files
clean_up <- . %>% 
  tidy(effects = "fixed") %>% 
  suppressWarnings() %>% 
  filter(term %in% c("effect_cattypical", "effect_con")) %>% 
  select(term, estimate, se = std.error)

# Function for printing unordered lists
print_status <- function(name) {
  filter(teams, team == name) %>% 
  pivot_longer(cols = -team, names_to = "var", values_to = "val") %>% 
  mutate(out = glue::glue("- {var}: {val}\n")) %>% 
  pull(out) 
}
```

@@

**Teams**:

```{r}
#| label: teams
#| echo: false
teams <- tribble(
  ~'team',                  ~"Reviewed", ~'Included', 
  "anomalocaris_ornata",      TRUE,           TRUE,
  "anthracoceros_coronata",   TRUE,           TRUE,
  "arapaima_modularis",       TRUE,           TRUE,
  "comanthina_maculatus",     TRUE,           TRUE,
  "cromileptes_saxatilis",    TRUE,           TRUE,
  "ctenosaura_limax",         TRUE,           FALSE,
  "gnathosaurus_canadensis",  FALSE,          FALSE,
  "gymnothorax_spinulosus",   FALSE,          FALSE,
  "haematopus_fossor",        TRUE,           TRUE,
  "lasionycteris_altavela",   TRUE,           TRUE,
  "linckia_nattereri",        FALSE,          FALSE,
  "lycodes_bradfieldi",       FALSE,          FALSE,
  "naso_cassivellaunos",      FALSE,          FALSE,
  "trapezia_cantonensis",     FALSE,          FALSE,
  "trigonias_lachneri",       FALSE,          FALSE,
  )

knitr::kable(teams)
```

**Current status**:

```{r}
#| label: status
#| echo: false
teams %>% 
  summarize(Reviewed = mean(Reviewed), Included = mean(Included)) %>% 
  pivot_longer(cols = everything(), names_to = " ", values_to = "%") %>% 
  mutate(`%` = round(`%` * 100, 2)) %>% 
  knitr::kable(format = "pipe")
```

@@

```{r}
#| label: print_anomalocaris_ornata
#| echo: false
#| results: 'asis'
print_status("anomalocaris_ornata")
```

```{r}
#| label: anomalocaris_ornata

# Analyst team setup
main.df <- read.csv2(here("data", "analyses", "jvc", 
  "anomalocaris_ornata", "MSA", "data", "data_frame.csv")
  )

df.int <- main.df %>%
  filter(keep == "yes") %>%  
  filter(condition == "NF") %>% 
  mutate(typicality = fct_relevel(typicality, "typical", "medium", "atypical"))

df.int$Mean_dB <- as.numeric(df.int$Mean_dB)

# F0
df.f0 <- main.df
df.f0 <- df.f0 %>%
  #filter(stress == "stressed") %>%
  filter(keep == "yes") %>% 
  filter(condition == "NF") %>%
  #filter(phoneme %in% c("AO","AW","IH","o","OEH","UH","AH","EH","EH?","u","a?","i","i?" )) %>% 
  gather(f0_point, f0, F0AtPoint1, F0AtPoint2, F0AtPoint3, F0AtPoint4,
         F0AtPoint5,F0AtPoint6,F0AtPoint7,F0AtPoint8,F0AtPoint9,F0AtPoint10)%>% 
  filter(f0 !="--undefined--")%>% 
  mutate(typicality = fct_relevel(typicality, "typical", "medium", "atypical")) %>% 
  group_by(voice_type, col_obj)

df.f0$f0 <- as.numeric(df.f0$f0)
outliers <- boxplot(df.f0$f0, plot=F)$out
f0.clean <- df.f0[-which(df.f0$f0 %in% outliers),]
f0.clean <- f0.clean %>% 
  ungroup() %>% 
  group_by(speaker) %>% 
  mutate(f0min = min(f0)) %>%
  mutate(f0sem=(12*log(f0 /f0min))/log(2)) %>% 
  ungroup()

under <- f0.clean %>% 
  filter(f0<150)
over <- f0.clean %>% 
  filter(f0>150)

# Vowel
vowel.df <- main.df
vowel.df$Duration_in_ms <- as.numeric(vowel.df$Duration_in_ms)
vowel.df <- vowel.df %>%
  filter(keep == "yes") %>%  
  filter(condition == "NF") %>% 
  filter(stress =="stressed") %>% 
  mutate(typicality = fct_relevel(typicality, "typical", "medium","atypical")) %>%
  filter(Duration_in_ms>40)

# FREQ MODELS
mod1 <- lmer(Mean_dB^2~typicality*col_obj+voice_type+(1+col_obj|speaker),df.int)
mod2 <- lmer(f0sem~col_obj*typicality+voice_type+(1+col_obj|speaker),under)
mod3 <- lmer(f0sem~col_obj*typicality+voice_type+(1+col_obj|speaker),over)
mod4 <- lmer(Duration_in_ms~typicality*col_obj+(1|Word)+(1|speaker),data = vowel.df)

#
# JVC: Setup and reanalyses
#

# Intensity
MSA_int_df <- df.int %>% 
  mutate(mean_db_2 = Mean_dB ^ 2, 
    db_z = (mean_db_2 - mean(mean_db_2)) / sd(mean_db_2), 
    effect_cat = C(typicality, treatment), 
    effect_cat = fct_relevel(effect_cat, "atypical"), 
    col_obj = as.factor(col_obj), 
    col_obj = C(col_obj, sum), 
    voice_type = as.factor(voice_type), 
    voice_type = C(voice_type, sum)
)

# Intensity model
anomalocaris_ornata_1_int_cat <- brm(
  db_z ~ effect_cat * col_obj + voice_type + 
    (1 + col_obj | speaker), 
  data = MSA_int_df, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", 
  file = here("data", "analyses", "models", "anomalocaris_ornata_1_int_cat")
  )

# Pitch "under"
MSA_under_df <- under %>% 
  mutate(f0sem_z = (f0sem - mean(f0sem)) / sd(f0sem), 
    effect_cat = C(typicality, treatment), 
    effect_cat = fct_relevel(effect_cat, "atypical"), 
    col_obj = as.factor(col_obj), 
    col_obj = C(col_obj, sum), 
    voice_type = as.factor(voice_type), 
    voice_type = C(voice_type, sum)
  )

# Pitch "under" model
anomalocaris_ornata_2_f0under_cat <- brm(
  f0sem_z ~ effect_cat * col_obj + voice_type + 
    (1 + col_obj | speaker), 
  data = MSA_under_df, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", 
  file = here("data", "analyses", "models", "anomalocaris_ornata_2_f0under_cat")
  )

# Pitch "over"
MSA_over_df <- over %>% 
  mutate(f0sem_z = (f0sem - mean(f0sem)) / sd(f0sem), 
    effect_cat = C(typicality, treatment), 
    effect_cat = fct_relevel(effect_cat, "atypical"), 
    col_obj = as.factor(col_obj), 
    col_obj = C(col_obj, sum), 
    voice_type = as.factor(voice_type), 
    voice_type = C(voice_type, sum)
  )

# Pitch "over" model
anomalocaris_ornata_3_f0over_cat <- brm(
  f0sem_z ~ effect_cat * col_obj + voice_type + 
    (1 + col_obj | speaker), 
  data = MSA_over_df, 
  cores = 4, threads = threading(2, grainsize = 100), 
  control = list(max_treedepth = 15), 
  backend = "cmdstanr", 
  file = here("data", "analyses", "models", "anomalocaris_ornata_3_f0over_cat")
  )

# Duration
MSA_durvowel_df <- vowel.df %>% 
  mutate(dur_z = (Duration_in_ms - mean(Duration_in_ms)) / sd(Duration_in_ms), 
    effect_cat = C(typicality, treatment), 
    effect_cat = fct_relevel(effect_cat, "atypical"), 
    col_obj = as.factor(col_obj), 
    col_obj = C(col_obj, sum)
  )

anomalocaris_ornata_4_durvowel_cat <- brm(
  dur_z ~ effect_cat * col_obj + 
    (1 | Word) + (1 | speaker), 
  data = MSA_durvowel_df, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", 
  file = here("data", "analyses", "models", "anomalocaris_ornata_4_durvowel_cat")
  )

@@

```{r}
#| label: print_anthracoceros_coronata
#| echo: false
#| results: 'asis'
print_status("anthracoceros_coronata")
```

```{r}
#| label: anthracoceros_coronata

data_long <- read_csv(here("data", "analyses", "jvc", "anthracoceros_coronata", 
  "data", "data_long.csv"))

# Fit LME models (dont converge and not used)
overall_models <- data_long %>% 
  group_by(variable) %>% 
  nest() %>% 
  mutate(model = map(data, ~ lmer(value ~ typ_mean + (1|speaker), data = .)),
         tidy = map(model, broom.mixed::tidy, effects = c("fixed", "ran_vals"), conf.int = TRUE, conf.level =.95)) %>% 
  unnest(tidy) %>% 
  select(-model)

# Standard lm
overall_models_lm <- data_long %>% 
  group_by(variable) %>% 
  nest() %>% 
  mutate(model = map(data, ~ lm(value ~ typ_mean, data = .)),
         tidy = map(model, tidy, conf.int = TRUE, conf.level =.95)) %>% 
  unnest(tidy) %>% 
  select(-data, -model)

#
# JVC: setup and refit
#
MSA_ac_all_df <- data_long %>% 
  group_by(variable) %>% 
  mutate(value_z = (value - mean(value, na.rm = T)) / sd(value, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(effect_con = (typ_mean - mean(typ_mean)) / sd(typ_mean))

# A_max_pitch
anthracoceros_coronata_1_pitchadj_con <- brm(
  value_z ~ effect_con, 
  data = filter(MSA_ac_all_df, variable == "A_max_pitch"), 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", 
  file = here("data", "analyses", "models", 
    "anthracoceros_coronata_1_pitchadj_con")
  )

# N_max_pitch
anthracoceros_coronata_2_pitchnoun_con <- brm(
  value_z ~ effect_con, 
  data = filter(MSA_ac_all_df, variable == "N_max_pitch"), 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", 
  file = here("data", "analyses", "models", 
    "anthracoceros_coronata_2_pitchnoun_con")
  )

# A_max_intens
anthracoceros_coronata_3_intadj_con <- brm(
  value_z ~ effect_con, 
  data = filter(MSA_ac_all_df, variable == "A_max_intens"), 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", 
  file = here("data", "analyses", "models", 
    "anthracoceros_coronata_3_intadj_con")
  )

# N_max_intens
anthracoceros_coronata_4_intnoun_con <- brm(
  value_z ~ effect_con, 
  data = filter(MSA_ac_all_df, variable == "N_max_intens"), 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", 
  file = here("data", "analyses", "models", 
    "anthracoceros_coronata_4_intnoun_con")
  )

# A_dur_log
anthracoceros_coronata_5_duradj_con <- brm(
  value_z ~ effect_con, 
  data = filter(MSA_ac_all_df, variable == "A_dur_log"), 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", 
  file = here("data", "analyses", "models", 
    "anthracoceros_coronata_5_duradj_con")
  )

# N_dur_log
anthracoceros_coronata_6_durnoun_con <- brm(
  value_z ~ effect_con, 
  data = filter(MSA_ac_all_df, variable == "N_dur_log"), 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", 
  file = here("data", "analyses", "models", 
    "anthracoceros_coronata_6_durnoun_con")
  )
```

@@

```{r}
#| label: print_arapaima_modularis
#| echo: false
#| results: 'asis'
print_status("arapaima_modularis")
```

```{r}
#| label: arapaima_modularis

data_manyspeech <- read.csv(here("data", "analyses", "jvc", 
  "arapaima_modularis", "sheet_data_pitch.csv"))

#convert factors and numeric
data_manyspeech$typicality <- factor(data_manyspeech$typicality)
data_manyspeech$target_colour <- factor(data_manyspeech$target_colour)
data_manyspeech$pitch_max_hz <- as.numeric(data_manyspeech$pitch_max_hz)
data_manyspeech$exclude <- factor(data_manyspeech$exclude)

#select variables to be used, exclude error items
clean_data <- data_manyspeech %>%
  select(condition, speaker, typicality, target_colour, pitch_max_hz, exclude) %>%
  filter(condition == "NF",
    exclude == "No")

#Main stats
summary_clean_data <- clean_data %>%
  group_by(speaker, typicality) %>%
  rstatix::get_summary_stats(pitch_max_hz)

#rename outcome variable 
names(summary_clean_data)[names(summary_clean_data) == 'mean'] <- 'mean_pitch'

#exclude three speakers who had typycality conditions < 6
clean_data_2 <- clean_data %>%
  filter(speaker != "EM",
         speaker != "IP",
         speaker != "JW_3")

#New main stats without 3 excluded participants
data_for_analysis <- clean_data_2 %>%
  group_by(speaker, typicality) %>%
  rstatix::get_summary_stats(pitch_max_hz)

names(data_for_analysis)[names(data_for_analysis) == 'mean'] <- 'mean_pitch'

#find ouliers
outliers <- data_for_analysis %>%
  group_by(typicality) %>%
  rstatix::identify_outliers(mean_pitch)
  #13 outlier data points were found

#continue without outliers
data_for_analysis_noOL <- data_for_analysis %>%
  filter(speaker != "AL",
         speaker != "JR",
         speaker != "PS",
         speaker != "TB")

# Original model
mod1_am <- ez::ezANOVA(data = data_for_analysis_noOL,
        wid = speaker,
        within = typicality,
        dv = mean_pitch,
        type = 3)

#
# JVC: setup df
#
MSA_arapaima_modularis_df <- data_for_analysis_noOL %>% 
  mutate(pitch_z = (mean_pitch - mean(mean_pitch)) / sd(mean_pitch), 
    effect_cat = C(typicality, treatment), 
    effect_cat = fct_relevel(effect_cat, "atypical"))

# Model
arapaima_modularis_1_f0_cat <- brm(
  pitch_z ~ effect_cat, 
  data = MSA_arapaima_modularis_df, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", 
  file = here("data", "analyses", "models", "arapaima_modularis_1_f0_cat")
  )
```

@@

```{r}
#| label: print_comanthina_maculatus
#| echo: false
#| results: 'asis'
print_status("comanthina_maculatus")
```

```{r}
#| label: comanthina_maculatus

# No code provided
MSA_comanthina_maculatus_df <- read_xlsx(here("data", "analyses", "jvc", 
  "comanthina_maculatus", "0 Clean Data.xlsx"), na = "--undefined--") %>% 
  select(key:typicality, 
    tonic_vowel_duration, tonic_vowel_intensity, tonic_vowel_F0) %>% 
  na.omit() %>% 
  filter(typicality != "medium") %>% 
  mutate(across(starts_with("tonic"), .fns = scale, .names = "{.col}_z")) %>% 
  mutate(effect_cat = as.factor(typicality), 
    effect_cat = C(effect_cat, treatment))

# Model
comanthina_maculatus_1_dur_cat <- brm(
  tonic_vowel_duration_z ~ effect_cat, 
  data = MSA_comanthina_maculatus_df, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "comanthina_maculatus_1_dur_cat")
  )

comanthina_maculatus_2_int_cat <- brm(
  tonic_vowel_intensity_z ~ effect_cat, 
  data = MSA_comanthina_maculatus_df, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "comanthina_maculatus_2_int_cat")
  )

comanthina_maculatus_3_f0_cat <- brm(
  tonic_vowel_F0_z ~ effect_cat, 
  data = MSA_comanthina_maculatus_df, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "comanthina_maculatus_3_f0_cat")
  )
```

@@

```{r}
#| label: print_cromileptes_saxatilis
#| echo: false
#| results: 'asis'
print_status("cromileptes_saxatilis")
```

```{r}
#| label: cromileptes_saxatilis

cromileptes_saxatilis_durs <- read_csv(here("data", "analyses", "jvc", "cromileptes_saxatilis", "processed_data", "NF_durations.csv")) %>% 
  filter(typicality != "medium")

mod_priors <- c(
  prior("normal(-1, 1)", class="Intercept"),
  prior("normal(0, 2)", class="b"),
  prior("student_t(3, 0, 1)", class="sd"),
  prior("lkj(2)", class="L")
)

# Original model
if(F) {
set.seed(12341234)
mod <- brm(colour_dur ~ 
             typicality + 
             (1 + typicality | target_colour) + 
             (1 | target_name) + 
             (1 | speaker),
           data=cromileptes_saxatilis_durs, cores=4,
           family=lognormal(),
           prior=mod_priors,
           control=list(adapt_delta=0.99,
                        max_treedepth=16),
           iter=4000,
           warmup=2000)
}

#
# JVC refits
#

MSA_cromileptes_saxatilis_df <- cromileptes_saxatilis_durs %>% 
  mutate(colour_dur_log = log(colour_dur), 
    colour_dur_z = (colour_dur_log - mean(colour_dur_log)) / sd(colour_dur_log), 
    effect_cat = as.factor(typicality), 
    effect_cat = C(effect_cat, treatment))

cromileptes_saxatilis_1_dur_cat <- brm(
  colour_dur_z ~ effect_cat + 
    (1 + typicality | target_colour) + 
    (1 | target_name) + 
    (1 | speaker), 
  data = MSA_cromileptes_saxatilis_df, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "cromileptes_saxatilis_1_dur_cat")
  )
```

@@

```{r}
#| label: print_ctenosaura_limax
#| echo: false
#| results: 'asis'
print_status("ctenosaura_limax")
```

```{r}
#| label: ctenosaura_limax

@@

```{r}
#| label: print_gnathosaurus_canadensis
#| echo: false
#| results: 'asis'
print_status("gnathosaurus_canadensis")
```

```{r}

@@

```{r}
#| label: print_gymnothorax_spinulosus
#| echo: false
#| results: 'asis'
print_status("gymnothorax_spinulosus")
```

@@

```{r}
#| label: print_haematopus_fossor
#| echo: false
#| results: 'asis'
print_status("haematopus_fossor")
```

@@

```{r}
#| label: print_lasionycteris_altavela
#| echo: false
#| results: 'asis'
print_status("lasionycteris_altavela")
```

@@

```{r}
#| label: print_linckia_nattereri
#| echo: false
#| results: 'asis'
print_status("linckia_nattereri")
```

@@

```{r}
#| label: print_lycodes_bradfieldi
#| echo: false
#| results: 'asis'
print_status("lycodes_bradfieldi")
```

@@

```{r}
#| label: print_naso_cassivellaunos
#| echo: false
#| results: 'asis'
print_status("naso_cassivellaunos")
```

@@

```{r}
#| label: print_trapezia_cantonensis
#| echo: false
#| results: 'asis'
print_status("trapezia_cantonensis")
```

@@

```{r}
#| label: print_trigonias_lachneri
#| echo: false
#| results: 'asis'
print_status("trigonias_lachneri")
```

@@

msa_models <- dir_ls(path = here("data", "analyses", "models"), 
  regexp = ".rds$") %>% 
  as_tibble() %>% 
  transmute(path = value, 
    mod_name = str_remove(path, here("data", "analyses", "models/")), 
    mod_name = str_remove(mod_name, ".rds"), 
    model = map(path, ~ readRDS(file = .))) %>% 
  separate(mod_name, 
    into = c("word1", "word2", "mod_n", "outcome", "typicality"), 
    sep = "_", remove = F) %>% 
  unite(group, word1, word2, sep = "_") %>% 
  select(group, mod_name:model) %>% 
  mutate(sum = map(model, clean_up)) %>% 
  suppressWarnings() 
```

@@

# Simple forest plot of the estimates +/- SE
msa_models %>% 
  unnest(sum) %>% 
  mutate(typicality_lab = if_else(typicality == "cat", 
    "Typicality = categorical", "Typicality = continuous"), 
    mod_name = fct_reorder(mod_name, estimate)) %>% 
  ggplot() + 
  facet_wrap(~ typicality_lab, ncol = 1, scales = "free") + 
  aes(x = estimate, y = mod_name) + 
  geom_vline(xintercept = 0, lty = 3) + 
  geom_segment(aes(x = estimate - se, xend = estimate + se, yend = mod_name), 
    color = "#cc0033", alpha = 0.5, size = 1.5, lineend = "round") + 
  geom_point(color = "#cc0033", pch = 21, stroke = 1.5, size = 1.6) + 
  labs(y = "Model", x = "Estimate ± SE") + 
  clean_theme() + 
  theme(strip.text.x = element_text(hjust = 0))
```
